---
title: "Getting starting with git and GitHub using RStudio"
author: "NCEAS"
maintainer: "Julien Brun"
last_updated_by: "Julien Brun"
output: 
  html_document:
    include:
      after_body: footer.html
    theme: "spacelab"
    # df_print: "paged"
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
params:
  output_dir: "docs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# rmarkdown::render("getting-started-with-git-rstudio.Rmd", output_dir = "docs")
```

<br>
<br>
This document is a compilation of [NCEAS](https://github.com/NCEAS/) training material on version control to create a 45-60 min crash course on getting started with version control for RStudio users. You will learn:

- how to setup git on your machine
- how to create repository on GitHub
- git basic workflow an manipulations using RStudio
- Collaborating using git and GitHub

<br>

<br>

```{r version control, child = './modules/version-control-intro.Rmd'}

```

---

<br>

```{r git intro, child = './modules/git-intro.Rmd'}

```


---

<br>

```{r setting computer, child = './modules/git-setting-computer.Rmd'}

```

---

<br>

```{r first repo, child = './modules/git-first-repo.Rmd'}

```

---

<br>

```{r git basics, child = './modules/git-workflow.Rmd'}

```


---

<br>

```{r git collaboration repo, child = './modules/git-collaboration.Rmd'}

```



---

<br>

```{r git conflicts repo, child = './modules/git-conflicts.Rmd'}

```

---

<br>

# References

## Using RStudio:

- R packages - Git and GitHub: http://r-pkgs.had.co.nz/git.html#git-init
- Happy Git and GitHub for the useR: http://happygitwithr.com/
 
## Mainly from the command line:
- Interactive git 101: [https://try.github.io/](https://try.github.io/)
- Very good tutorial about git: [https://www.atlassian.com/git/tutorials/what-is-version-control](https://www.atlassian.com/git/tutorials/what-is-version-control)
- Git tutorial geared towards scientists: [http://nyuccl.org/pages/gittutorial/](http://nyuccl.org/pages/gittutorial/)
- Short intro to git basics: [https://github.com/mbjones/gitbasics](https://github.com/mbjones/gitbasics)
- Git documentation about the basics: [http://gitref.org/basic/](http://gitref.org/basic/)
- Git documentation - the basics: [https://git-scm.com/book/en/v2/Getting-Started-Git-Basics](https://git-scm.com/book/en/v2/Getting-Started-Git-Basics)
- Git terminology: [https://www.atlassian.com/git/glossary/terminology](https://www.atlassian.com/git/glossary/terminology)
- In trouble, guide to know what to do: [http://justinhileman.info/article/git-pretty/git-pretty.png](http://justinhileman.info/article/git-pretty/git-pretty.png)
- Want to undo something? <https://github.com/blog/2019-how-to-undo-almost-anything-with-git> 
- Git terminology: <https://www.atlassian.com/git/glossary/terminology>
- 8 tips to work better with git: <https://about.gitlab.com/2015/02/19/8-tips-to-help-you-work-better-with-git/>
- GitPro book (2nd edition): <https://git-scm.com/book/en/v2>


## GitHub Workflow

- GitHub:
   - guides on how to use GitHub: [https://guides.github.com/](https://guides.github.com/)
   - GitHub from RStudio: [http://r-pkgs.had.co.nz/git.html#git-pull](http://r-pkgs.had.co.nz/git.html#git-pull)
- Forking:
   - [https://help.github.com/articles/fork-a-repo/](https://help.github.com/articles/fork-a-repo/)
   - [https://guides.github.com/activities/forking/](https://guides.github.com/activities/forking/)
- Comparison of git repository host services: <https://www.git-tower.com/blog/git-hosting-services-compared/>
- Branches
   - interactive tutorial on branches: <http://learngitbranching.js.org/>
   - using git in a collaborative environment: <https://www.atlassian.com/git/tutorials/comparing-workflows/centralized-workflow>
 